---
title: "Refresher QuiZ"
tutorial:
  id: "Quiz1"
output: learnr::tutorial
version: 1.0
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

### Quiz

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("1.Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("2.Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE),
    answer("ggplot2",correct = TRUE)
  ),
  question("3.What is the function to find the # of rows and columns of a data frame?",
    answer("dim", correct = TRUE),
    answer("length"),
    answer("nrow"),
    answer("ncol")
  ),
  question("4.Which of these options is correct assignment statement?",
    answer("C<-6"),
    answer("A=7"),
    answer("D<-5+7"),
    answer("All of the above",correct = TRUE)
  ),
  question("5.In R the following are all atomic data types EXCEPT: (Select all that apply)",
    answer("list",correct = TRUE),
    answer("array",correct = TRUE),
    answer("matrix",correct = TRUE),
    answer("table")
  ),
  question("6.If I execute the expression x <- 4 in R, what is the class of the object x as determined by the 'class()' function?",
    answer("numeric",correct = TRUE),
    answer("vector"),
    answer("data frame"),
    answer("tibble")
  ),
  question("7.What could be used to find the indices of a vector/column in a data frame that satisfy a condition?",
    answer("subset"),
    answer("which",correct = TRUE),
    answer("row.names"),
    answer("colnames")
  ),
  question("8.What is the class of the object defined by the expression x <- c(4, “a”, TRUE)",
    answer("vector"),
    answer("logical"),
    answer("character",correct = TRUE),
    answer("string")
  ),
  
  question("9.This is TRUE about data frames",
    answer("Can only have same data type in all rows across a column", correct = TRUE),
    answer("Can have different lengths/row size for each column")
    
  ),
  question("10.What is the result of this operation c(1,3,4)+c(1,2)",
    answer("2 5 5",correct = TRUE),
    answer("ERROR"),
    answer("Warning: longer object length is not a multiple of shorter object length",correct = TRUE),
    answer("None of the Above")
  )
  
)
```

###  Exercise
11.Write the R code required to add two plus two:

```{r e1, exercise=TRUE}

```

12.Suppose we have a list defined as x <- list(2, "a", "b", TRUE). What does x[[1]] give me?

```{r e2, exercise=TRUE, exercise.lines = 3,exercise=TRUE}

print("TYPE YOUR ANSWER HERE")
```

13.Suppose we have a vector x <- c(17, 14, 4, 5, 13, 12, 10) and I want to set all elements of this vector that are greater than 10 to be equal to 4. What R code achieves this?

```{r e3, exercise=TRUE}

```

14.Modify this code so that it prints only the first 5 rows of the mtcars dataset:

```{r e4, exercise=TRUE,exercise.eval=FALSE}
head(mtcars)
```

15.What is the value of hp(Horsepower) in $mtcars$ for 32nd  row?

```{r e5, exercise=TRUE,exercise.eval=FALSE}

```

16.How many missing values are in the $mpg$column of $mtcars$ data frame?

```{r e6, exercise=TRUE,exercise.eval=FALSE}

```

17.Plot $mpg$,$cyl$ for data $mtcars$ using $ggplot2$?

```{r e7, exercise=TRUE,exercise.eval=FALSE}

```

18.Plot $mpg$,$wt$ for data $mtcars$ using $ggplot2$?

```{r e8, exercise=TRUE,exercise.eval=FALSE}

```

19.What is the command/function for installing a package in R from CRAN?

```{r e9, exercise=TRUE,exercise.eval=FALSE}
print("YOUR ANSWER HERE")

```

20.What is the command/function for loading a package in R?

```{r e10, exercise=TRUE,exercise.eval=FALSE}
print("YOUR ANSWER HERE")

```
